\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity

### 2021-09-08 Chapter_1/04_Manuscript/Manuscript_Support_2021-08-30.tex
Various updates

%------------------------------------------------------------------------------
%	Appendix S3: Movement Model interpretation
%------------------------------------------------------------------------------
\newpage
% \newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Movement Model Interpretation}
To ease with the interpretation of the most parsimonious movement model, we
followed recommendations published in \cite{Fieberg.2020} and produced a series
of plots highlighting how the habitat and movement kernel depended on covariate
values (\Cref{Interpretation}). To visualize the movement kernel and its
interactions with other covariates, we used model estimates and updated our
tentative distribution parameters for turning angles (von Mises distribution
with concentration \(\kappa = 0\)) and step lengths (gamma distribution with
scale \(\theta\) = 6'308 and shape \(k\) = 0.37) by applying the function
\textsf{update\_vonmises()} from the R-package \textsf{amt} \citep{Amt.2019}.
This allowed us to compute probability densities of turning angles and step
lengths under varying values of the associated covariates, while holding all
other covariates constant (\Cref{Interpretation}, a1-a8). Moreover, we
investigated the habitat kernel by computing relative selection strengths (RSS)
between a set of steps where values of the covariate of interest was varied to a
reference step where the covariate value was fixed to its centered value. To
illustrate model uncertainty, we also generated large-sample confidence
intervals using standard errors associated with each model estimate
(\Cref{Interpretation}, b1-b5).

@@

%------------------------------------------------------------------------------
%	Appendix S4: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
    steps, respectively. The left panel (a1, a2, a3) was generated based on
    simulations initiated within the main study area, the right panel (b1, b2,
    b3) was generated based on simulations initiated within the buffer area. To
    produce the heatmap presented in the main manuscript (Figure 5), we tallied
    the values from maps a3 and b3.}
    \label{Heatman}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S5: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced when considering (a) 125, (b)
    500, (c) and 2000 simulated steps, respectively. A high betweenness score
    indicates that the respective area has a high importance for linking other
    regions in the study area.}
    \label{Betweenness}
  \end{center}
\end{figure}
\restoregeometry

>>>>

%------------------------------------------------------------------------------
%	Appendix S3: Most Parsimonious Model
%------------------------------------------------------------------------------
\newpage
\begin{table}
  \begin{center}
  \caption{Most parsimonious movement model for dispersing wild dogs. The
  movement kernel describes preferences of dispersers with regards to movement
  behavior (may also be viewed as movement capability), whereas the habitat
  kernel describes preferences with respect to habitat conditions. Interactions
  between the two kernels indicate that the two kernels are not independent,
  meaning that movement preferences are contingent on habitat conditions. Note
  that all covariates were standardized to a mean of zero and standard deviation
  of 1. Plots to aid with the interpretation of this model are given in Appendix
  S2.}
  \label{MovementModelNumbers}
  \resizebox{\textwidth}{!} {
    \begin{threeparttable}
      \begin{tabular}{llrrrc}
        \toprule
        Kernel & Covariate & Coefficient & SE & p-value & Sign. \\
        \midrule
        \multirow{5}{*}{Habitat Kernel}
         & Water & -0.546 & 0.112 & \(<\) 0.001 & *** \\
         & DistanceToWater \textsuperscript{0.5} & -0.390 & 0.231 & 0.092 & * \\
         & Woodland & -0.364 & 0.086 & \(<\) 0.001 & *** \\
         & Shrubs/Grassland & 0.288 & 0.092 & 0.002 & *** \\
         & HumanInfluence & -0.535 & 0.229 & 0.019 & ** \\
        \hdashline
        \multirow{6}{*}{Movement Kernel}
         & sl & 0.075 & 0.037 & 0.042 & ** \\
         & cos(ta) & 0.105 & 0.031 & 0.001 & *** \\
         & log(sl) & 0.146 & 0.051 & 0.004 & *** \\
         & cos(ta) : sl & 0.049 & 0.026 & 0.064 & * \\
         & cos(ta) : log(sl) & 0.076 & 0.026 & 0.003 & *** \\
         & sl : LowActivity & -0.917 & 0.113 & \(<\) 0.001 & *** \\
        \hdashline
        \multirow{5}{*}{Interactions}
         & sl : Water & -0.305 & 0.076 & \(<\) 0.001 & *** \\
         & sl : Woodland & -0.089 & 0.039 & 0.023 & ** \\
         & sl : Shrubs/Grassland & 0.124 & 0.058 & 0.032 & ** \\
         & sl : DistanceToWater \textsuperscript{0.5} & -0.058 & 0.031 & 0.056 & * \\
         & cos(ta) : HumanInfluence & -0.040 & 0.022 & 0.070 & * \\
         & cos(ta) : DistanceToWater \textsuperscript{0.5} & 0.063 & 0.026 & 0.017 & ** \\
         \bottomrule
      \end{tabular}
       \begin{tablenotes}
         \item \textit{Significance codes: * \(p < 0.10\) \quad ** \(p < 0.05\)
         \quad *** \(p < 0.01\)}
       \end{tablenotes}
    \end{threeparttable}
    }
  \end{center}
\end{table}

%------------------------------------------------------------------------------
%	Appendix S4: Movement Model interpretation
%------------------------------------------------------------------------------
\newpage
% \newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Movement Model Interpretation}
To ease with the interpretation of the most parsimonious movement model, we
followed recommendations published in \cite{Fieberg.2020} and produced a series
of plots highlighting how the habitat and movement kernel depended on covariate
values (\Cref{Interpretation}). To visualize the movement kernel and its
interactions with other covariates, we used model estimates and updated our
tentative distribution parameters for turning angles (von Mises distribution
with concentration \(\kappa = 0\)) and step lengths (gamma distribution with
scale \(\theta\) = 6'308 and shape \(k\) = 0.37) by applying the function
\textsf{update\_vonmises()} from the R-package \textsf{amt} \citep{Amt.2019}.
This allowed us to compute probability densities of turning angles and step
lengths under varying values of the associated covariates, while holding all
other covariates constant (\Cref{Interpretation}, a1-a8). Moreover, we
investigated the habitat kernel by computing relative selection strengths (RSS)
between a set of steps where values of the covariate of interest was varied to a
reference step where the covariate value was fixed to its centered value. To
illustrate model uncertainty, we also generated large-sample confidence
intervals using standard errors associated with each model estimate
(\Cref{Interpretation}, b1-b5).

@@

%------------------------------------------------------------------------------
%	Appendix S5: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
    steps, respectively. The left panel (a1, a2, a3) was generated based on
    simulations initiated within the main study area, the right panel (b1, b2,
    b3) was generated based on simulations initiated within the buffer area. To
    produce the heatmap presented in the main manuscript (Figure 5), we tallied
    the values from maps a3 and b3.}
    \label{Heatman}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S6: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced when considering (a) 125, (b)
    500, (c) and 2000 simulated steps, respectively. A high betweenness score
    indicates that the respective area has a high importance for linking other
    regions in the study area.}
    \label{Betweenness}
  \end{center}
\end{figure}
\restoregeometry
